\textbf{Title}

### 2015-05-04 paper/draft_2.tex
modified tables in draft

Before delving deeper into the two denoising tasks, we first present a brief overview of wavelet estimators. These estimators have become extremely popular in nonparametric regression problems following the seminal paper by Donoho \& Johnstone (1994). Not only are wavelet methods locally adaptive in the sense that they achieve the optimal minimax rate over a wide variety of functions, but they are also computationally faster than many other adaptive methods such as variable-bandwidth kernel methods [antoniadis 2001]. While classical thresholding estimators have been shown to possess optimal asymptotic properties, an extensive simulation study by Antoniadis et al. (2001) has demonstrated that various Bayesian shrinkage methods can often outperform thresholding methods in finite samples, where performance is measured by mean squared error (MSE). However, many existing Bayesian wavelet methods are often computationally intensive, and may not be practical for large scale applications. Furthermore, it is not easy to apply the same thresholding or Bayesian shrinkage rules to other nonparametric regression problems, two of which we subsequently describe. On the other hand, our method is computationally faster than previous Bayesian methods while still possessing good finite sample performance, and use ASH as the common shrinkage procedure in both the problems.\bigskip\\

@@

The flexibility and computational efficiency of this shrinkage procedure is immediately obvious, which motivates us to extend this method to the more complex wavelet setting described here. Gaussian mixture priors can effectively approximate any unimodal distribution, allowing us to apply this single shrinkage procedure to the two problems we will be focusing on. At the same time, we can speed up the entire signal denoising problem via likelihood approximations (discussed in the next section), allowing our method to be computationally efficient without compromising too much accuracy. Furthermore, it should be noted that many wavelet methods require the specification of a primary resolution level as an extra parameter, which could substantially influence the accuracy of the method. On the other hand, we can apply ASH to every resolution in the wavelet transformation, sparing the need for such a parameter. For an in-depth understanding of the original motivations and applications of ASH, see Stephens (??). With the main shrinkage method accounted for, we will now proceed to explore the two aforementioned problems in detail. Note that one only needs to supply a vector of estimates $\hat{\Gb}$ and their standard errors se$(\hat{\Gb})$ to ASH to obtain posterior estimates; hence, we will focus on obtaining these estimates and standard errors when describing our methods.

@@

To describe the approximation process in more detail, we drop the subscripts for notational convenience. One direct approximation of the likelihood for $\Ga$ is $\phi(\Ga;\hat{\Ga},\mathbb{V}(\hat{\Ga}))$ for some appropriate estimator $\hat{\Ga}$. This choice of parameters for the Gaussian approximation is also appropriate in the sense that it minimizes the Kullback-Leibler divergence between a Gaussian distribution and the likelihood for $\Ga$ (also known as moment matching).\bigskip\\
We next consider appropriate estimators for the parameters $\Ga$ and $\sqrt{\mathbb{V}(\hat{\Ga})}$. The obvious choice would be the MLE of $\Ga$ and its asymptotic standard error respectively, given by

@@

where $S$ is the number of successes in the binomial setup, and $F=N-S$ is the number of failures (in our case the even locations would be successes and odd locations failures). The MLE has one notable drawback however, in that it cannot deal well with extreme cases. This would in turn affect the normal approximation in a non-negligible way. To improve the accuracy of the approximation at the endpoints of the binomial distribution (ie. when we have $\hat{p}=0$ or $N$, so that $\hat{\Ga}=-\infty$ or $\infty$ respectively), while at the same time ensuring that $\hat{\Ga}$ is approximately unbiased for $\Ga$ so that moment matching still makes sense, we propose a mix of Berkson's estimator and Tukey's estimator. Specifically, our final estimators for $\Ga$ and its standard error are given by

@@

To highlight the flexibility of our method, we first present the results for the homoskedastic case. Here we compare our method, which does not assume homoskedasticity (and hence jointly estimates the mean and variance), to various popular wavelet based methods which do assume homoskedasticity. For illustration purposes, we also include the case where our method does assume homoskedasticity and takes an estimated $\s$ as input (this is also a feature of our method). Note that we use a second order difference estimate of the variance as described by Hall et al. (1990) rather than the median absolute deviation (MAD) estimate that is commonly used in thresholding methods for computational simplicity. The practical difference between these two estimators is small, unless the mean function is extremely irregular. Specifically, we include the following methods for this particular simulation study:

@@

\item TI thresholding using variance estimated by running MAD, Symmlet 8 basis (denoted by TI, RMAD, Symm8). See Gao (1997)
\item TI thresholding using variance estimated by SMASH, Symmlet 8 basis (denoted by TI, SMASH, Symm8)

@@

\item TI thresholding using MAD estimator, Symmlet 8 basis (denoted by TI, homo, Symm8). See Coifman \& Donoho (1995)

@@

@@

\item Bayesian shrinkage using MAD estimator, Symmlet 8 basis (denoted by PostMean, homo, Symm8). See Clyde \& George (1999,2000)

@@

\item TI thresholding given true variance, Symmlet 8 basis (denoted by TI, truth, Symm8)

@@

Here compare our method mainly against TI thresholding, which often produced the smallest mean squared error (MSE) amongst all the methods discussed in the extensive simulation study conducted by Antoniadis et al. (2001). At the same time, we included SureShrink as it performs well in terms of mean square bias. We also compared our method against two other Bayesian approaches, of which the method described in Clyde \& George (1999,2000) was also included in Antoniadis et al. (2001) and performed well in terms of MSE. The other Bayesian approach, EbayesThresh, is more recent and and hence included as part of our study. Note that methods (1)-(4) do not assume homoskedastic errors and perform their own variance estimation, while methods (5)-(9) all estimate a constant variance. Methods (10) and (11) are provided the true variance function and are included as benchmarks. Tables \ref{table:homo1} and \ref{table:homo3} displays the mean integrated squared error (MISE) of various methods for the 7 test functions and 2 SNRs mentioned above. Here MISE is defined as
\begin{eqnarray}\label{eq:mise}
MISE=\sum_{r=1}^R{\frac{10000*\sum_{i=1}^n(\hat{\mu}^{(r)}_i-\mu_i)^2}{\sum_{i=1}^n \mu_i^2}}
, which is simply the standard MSE rescaled in order to produce more comparable numbers. Here $R$ is the number of runs in each simulation (100 in our study) and $n$ is the sample size.

@@

SMASH, joint, Haar & 57.1 & 146.5 & 65.0 & 50.6 & 76.8 & 24.1 & 8.2 \\
  SMASH, joint, Symm8 & 60.1 & 152.7 & 97.7 & 49.5 & 53.4 & 35.5 & 7.7 \\
  TI, RMAD, Symm8 & 84.0 & 253.7 & 152.2 & 66.7 & 70.2 & 42.0 & 8.6 \\
  TI, SMASH, Symm8 & 79.2 & 218.8 & 144.9 & 65.7 & 67.7 & 40.7 & 8.4 \\
  SMASH, homo, Symm8 & 61.0 & 154.9 & 100.2 & 50.1 & 54.9 & 35.8 & 7.8 \\
  TI, homo, Symm8 & 82.7 & 235.5 & 150.5 & 66.7 & 68.4 & 41.4 & 8.5 \\
  Ebayes, homo, Symm8 & 70.7 & 152.2 & 98.0 & 52.5 & 51.5 & 37.9 & 8.1 \\
  SURE, homo, Symm8 & 369.1 & 418.1 & 301.4 & 482.4 & 275.8 & 272.1 & 97.4 \\
  PostMean, homo, Symm8 & 101.4 & 185.1 & 113.0 & 86.2 & 70.5 & 53.2 & 13.3 \\
  SMASH, truth, Symm8 & 60.9 & 153.6 & 100.0 & 50.1 & 54.9 & 35.5 & 7.7 \\
  TI, truth, Symm8 & 83.1 & 234.7 & 150.8 & 67.1 & 69.1 & 41.3 & 8.5 \\

@@

\caption{MISEs of various methods for iid Gaussian errors, SNR=1}

@@

SMASH, joint, Haar & 11.8 & 18.4 & 7.4 & 10.3 & 18.0 & 3.6 & 1.7 \\
  SMASH, joint, Symm8 & 9.8 & 26.2 & 23.9 & 8.3 & 9.8 & 5.8 & 1.2 \\
  TI, RMAD, Symm8 & 10.9 & 33.7 & 30.7 & 9.4 & 13.5 & 6.6 & 1.5 \\
  TI, SMASH, Symm8 & 10.2 & 24.0 & 26.7 & 9.2 & 10.8 & 6.0 & 1.4 \\
  SMASH, homo, Symm8 & 9.8 & 22.4 & 22.9 & 8.3 & 9.2 & 5.6 & 1.2 \\
  TI, homo, Symm8 & 10.9 & 27.3 & 30.4 & 9.4 & 10.8 & 6.4 & 1.5 \\
  Ebayes, homo, Symm8 & 10.8 & 24.8 & 23.3 & 9.0 & 9.3 & 5.9 & 1.3 \\
  SURE, homo, Symm8 & 43.5 & 65.0 & 54.0 & 57.3 & 40.3 & 37.3 & 11.3 \\
  PostMean, homo, Symm8 & 15.2 & 30.9 & 26.8 & 13.1 & 12.7 & 9.0 & 2.0 \\
  SMASH, truth, Symm8 & 9.7 & 21.4 & 21.5 & 8.3 & 9.2 & 5.5 & 1.2 \\
  TI, truth, Symm8 & 10.9 & 26.1 & 29.7 & 9.4 & 10.8 & 6.4 & 1.5 \\

@@

\caption{MISEs of various methods for iid Gaussian errors, SNR=3}

@@

SMASH, joint, Haar & 108.5 & 282.2 & 112.4 & 86.9 & 113.7 & 62.5 & 15.5 \\
  SMASH, joint, Symm8 & 117.4 & 264.4 & 147.1 & 95.5 & 87.1 & 76.6 & 13.8 \\
  TI, RMAD, Symm8 & 191.9 & 268.6 & 168.5 & 154.0 & 107.1 & 90.9 & 22.5 \\
  TI, SMASH, Symm8 & 171.5 & 410.9 & 217.8 & 123.6 & 120.3 & 85.0 & 16.5 \\
  SMASH, homo, Symm8 & 413.7 & 501.7 & 356.1 & 553.6 & 314.7 & 296.9 & 106.1 \\
  TI, homo, Symm8 & 2007.9 & 1553.2 & 1416.9 & 3170.2 & 1460.2 & 1663.8 & 644.0 \\
  SMASH, truth, Symm8 & 115.6 & 221.4 & 128.4 & 93.1 & 74.6 & 77.5 & 13.7 \\
  TI, truth, Symm8 & 188.4 & 336.0 & 194.8 & 124.7 & 101.1 & 86.3 & 17.1 \\

@@

\caption{MISEs of various methods for variance function V2 as in Cai \& Wang (2008), SNR=1, Gaussian errors}

@@

SMASH, joint, Haar & 22.0 & 49.7 & 19.1 & 16.9 & 23.3 & 10.2 & 3.0 \\
  SMASH, joint, Symm8 & 20.4 & 59.2 & 40.0 & 14.3 & 11.7 & 18.7 & 2.7 \\
  TI, RMAD, Symm8 & 25.2 & 53.5 & 35.6 & 19.4 & 16.7 & 17.4 & 3.8 \\
  TI, SMASH, Symm8 & 24.3 & 64.7 & 43.5 & 16.1 & 14.4 & 18.9 & 3.3 \\
  SMASH, homo, Symm8 & 50.8 & 64.1 & 58.5 & 65.2 & 39.9 & 37.7 & 12.6 \\
  TI, homo, Symm8 & 225.3 & 174.0 & 159.5 & 354.4 & 156.5 & 186.0 & 71.8 \\
  SMASH, truth, Symm8 & 20.0 & 43.6 & 31.0 & 13.9 & 9.1 & 19.2 & 2.6 \\
  TI, truth, Symm8 & 25.9 & 66.6 & 42.8 & 17.1 & 10.0 & 22.2 & 3.6 \\

@@

\caption{MISEs of various methods for variance function V2 as in Cai \& Wang (2008), SNR=3, Gaussian errors}

@@

SMASH, joint, Haar & 223.1 & 650.9 & 275.9 & 233.6 & 232.6 & 148.0 & 47.4 \\
  SMASH, joint, Symm8 & 231.7 & 606.4 & 293.6 & 263.1 & 194.9 & 154.4 & 44.5 \\
  TI, RMAD, Symm8 & 1621.6 & 1464.5 & 1221.0 & 2543.6 & 1197.5 & 1334.5 & 512.2 \\
  TI, SMASH, Symm8 & 335.9 & 798.1 & 422.0 & 385.4 & 274.6 & 207.8 & 62.5 \\
  SMASH, homo, Symm8 & 1242.1 & 1199.3 & 940.4 & 1836.5 & 910.0 & 973.8 & 366.3 \\
  TI, homo, Symm8 & 3289.2 & 2543.4 & 2310.3 & 5206.6 & 2404.7 & 2731.0 & 1060.4 \\
  SMASH, truth, Symm8 & 114.0 & 633.3 & 214.9 & 115.9 & 100.6 & 81.5 & 15.6 \\
  TI, truth, Symm8 & 171.0 & 799.0 & 324.7 & 170.4 & 140.0 & 95.0 & 18.6 \\

@@

\caption{MISEs of various methods for the Bumps variance function, SNR=1, Gaussian errors}

@@

SMASH, joint, Haar & 34.9 & 137.1 & 56.0 & 32.9 & 46.9 & 20.5 & 6.9 \\
  SMASH, joint, Symm8 & 29.4 & 122.2 & 71.3 & 33.8 & 30.8 & 28.7 & 5.9 \\
  TI, RMAD, Symm8 & 174.8 & 183.1 & 153.4 & 286.2 & 137.0 & 152.1 & 57.4 \\
  TI, SMASH, Symm8 & 41.4 & 148.1 & 86.5 & 49.2 & 41.5 & 35.5 & 8.5 \\
  SMASH, homo, Symm8 & 141.3 & 167.3 & 127.7 & 209.1 & 112.9 & 114.0 & 41.6 \\
  TI, homo, Symm8 & 366.6 & 286.7 & 259.9 & 580.2 & 264.8 & 304.2 & 118.0 \\
  SMASH, truth, Symm8 & 14.9 & 162.9 & 67.1 & 16.9 & 16.0 & 13.2 & 2.5 \\
  TI, truth, Symm8 & 17.1 & 242.4 & 82.9 & 23.0 & 20.7 & 16.8 & 2.9 \\

@@

\caption{MISEs of various methods for the Bumps variance function, SNR=3, Gaussian errors}

@@

Summarizing the simulation studies conducted so far, we have demonstrated that our method does a reasonable job of mean and variance estimation for a variety of situations in the Gaussian case. As such, we now turn our attention to the Poisson case. For this simulation study, we considered different test functions and Poisson intensities for a given sample size of $n=1024$ as in Timmermann \& Nowak (1999) and Fryzlewicz \& Nason (2004), over 100 independent runs. Specifically, the ``Spikes'', ``Angles'', ``Bursts'',``Clipped Blocks'',``Bumps'' and ``Heavisine'' functions were chosen. The first 5 were part of a simulation study by Besbeas et al. (2004), and the ``Heavisine'' function was considered by Fryzlewicz \& Nason (2004). These test functions were then shifted and scaled to have (min,max) intensities of (0.01,3), (1/8,8) and (1/128,8), of which the latter two were the values used in Fryzlewicz \& Nason (2004). The low intensity scenario of (0.01,3) was chosen to reflect the small number of counts often present in certain types of high-throughput sequencing data, an application we will demonstrate in more detail later on. To assess the performance of our method, we used the same MISE as defined above for the Gaussian case, and considered the following methods in our simulation study:

@@

\item Conditional variance stabilization with the non-decimated wavelet transform (denoted by CVS). See Jansen (2006).

@@

The Haar-Fisz transform uses 50 external cyclespins as suggested by Fryzlewicz \& Nason (2004). The Anscombe transformations use the Symmlet 8 basis, while the Haar-Fisz transformation and CVS use the Symmlet 10 basis, as recommended by the corresponding software. Except for BMSM and our method (which are entirely adaptive), we considered primary resolution levels of 5,6 and 7 for all other methods. We present the MISEs for test functions ``Angles'' and ``Bumps'' in Tables \ref{table:pois_angles} and \ref{table:pois_bumps} respectively; full simulation results can be found in Appendix \ref{}.\bigskip\\

@@

SMASH & 145.3 & 68.5 & 10.2 \\
  Haar-Fisz & 369.5 & 140.4 & 9.8 \\
  Anscombe, universal & 459.0 & 163.7 & 10.1 \\
  Anscombe, CV & 458.8 & 162.6 & 10.1 \\
  Haar thresholds & 295.8 & 168.3 & 89.4 \\
  CVS & 5201.1 & 1083.5 & 122.8 \\
  BMMIM & 277.2 & 110.1 & 18.1 \\
  BMSM & 147.4 & 73.9 & 10.5 \\

@@

\caption{MISEs of various methods for the Angles function for Poisson data}

>>>>

Before delving deeper into the two denoising tasks, we first present a brief overview of wavelet estimators. These estimators have become extremely popular in nonparametric regression problems following the seminal paper by Donoho \& Johnstone (1994). Not only are wavelet methods locally adaptive in the sense that they achieve the optimal minimax rate over a wide variety of functions, but they are also computationally faster than many other adaptive methods such as variable-bandwidth kernel methods [antoniadis 2001]. While classical thresholding estimators have been shown to possess optimal asymptotic properties, an extensive simulation study by Antoniadis et al. (2001) has demonstrated that various Bayesian shrinkage methods are usually more data adaptive than thresholding methods in finite samples, outperforming the latter in terms of mean squared error (MSE). However, many existing Bayesian wavelet methods are often computationally intensive, and may not be practical for large scale applications. Furthermore, it is not easy to apply the same thresholding or Bayesian shrinkage rules to other nonparametric regression problems, two of which we subsequently describe. On the other hand, our method is computationally faster than previous Bayesian methods while still possessing good finite sample performance, and uses ASH as the common shrinkage procedure in both the problems.\bigskip\\

@@

The flexibility and computational efficiency of ASH is immediately obvious, which motivates us to extend this method to the more complex wavelet setting described here. As with many other Bayesian procedures, ASH borrows information across all available data, and is hence extremely data adaptive. At the same time, the key advantage of ASH over other Empirical Bayes procedures such as EbayesThresh [Johnstone \& Silverman (2005)] and the commonly used ``spike-and-slab'' prior (is there a name for this?) is that it allows for variable variances as input, a feature that the latter methods lack. This is also the primary reason we can use ASH as the only shrinkage procedure in both the problems described above. Furthermore, Gaussian mixture priors can effectively approximate any unimodal distribution, allowing for a more flexible prior than many other procedures. At the same time, we can speed up the entire signal denoising problem via likelihood approximations (discussed in the next section), allowing our method to be computationally efficient without compromising too much accuracy. It should be noted that typical wavelet methods require the specification of a primary resolution level as an extra parameter, which could substantially influence the accuracy of the method. However, we are able to apply ASH to every resolution in the wavelet transformation, sparing the need for such a parameter. For an in-depth understanding of the original motivations and applications of ASH, see Stephens (??). With the main shrinkage method accounted for, we will now proceed to explore the two aforementioned problems in detail. Note that one only needs to supply a vector of estimates $\hat{\Gb}$ and their standard errors se$(\hat{\Gb})$ to ASH to obtain posterior estimates; hence, we will focus on obtaining these estimates and standard errors when describing our methods.

@@

To describe the approximation process in more detail, we drop the subscripts for notational convenience. One direct approximation of the likelihood for $\Ga$ is the Laplace approximation, which results in the Gaussian likelihood given by $\phi(\Ga;\hat{\Ga}_{MLE},\mathbb{V}(\hat{\Ga}_{MLE}))$. Here $\phi$ is the normal density function, and $\hat{\Ga}_{MLE}$ is the maximum likelihood estimator. We would then estimate $\mathbb{V}(\hat{\Ga}_{MLE})$ by the square of the asymptotic standard deviation for $\hat{\Ga}_{MLE}$. Specifically,
% for some appropriate estimator $\hat{\Ga}$. This choice of parameters for the Gaussian approximation is also appropriate in the sense that it minimizes the Kullback-Leibler divergence between a Gaussian distribution and the likelihood for $\Ga$ (also known as moment matching).\bigskip\\
%We next consider appropriate estimators for the parameters $\Ga$ and $\sqrt{\mathbb{V}(\hat{\Ga})}$. The obvious choice would be the MLE of $\Ga$ and its asymptotic standard error respectively, given by

@@

where $S$ is the number of successes in the binomial setup, and $F=N-S$ is the number of failures (in our case the even locations would be successes and odd locations failures). The MLE has one notable drawback however, in that it cannot deal well with extreme cases. This would in turn affect the likelihood approximation in a non-negligible way. To improve the accuracy of the approximation at the endpoints of the binomial distribution (ie. when we have $\hat{p}=0$ or $N$, so that $\hat{\Ga}=-\infty$ or $\infty$ respectively), we instead aim to find a suitable estimator $\hat{\Ga}$ for $\Ga$. Next, we approximate the distribution of $\hat{\Ga}$ by a Gaussian distribution, so that the likelihood for $\Ga$ is automatically Gaussian, given by $\phi(\Ga;\hat{\Ga},\mathbb{V}(\hat{\Ga}))$. To that end, we propose a mix of Berkson's estimator and Tukey's estimator as suggested in Gart \& Zweifel (1967). Specifically, our final estimators for $\Ga$ and its standard error are given by

@@

To highlight the flexibility of our method, we first present the results for the homoskedastic case. Here we compare our method, which does not assume homoskedasticity (and hence jointly estimates the mean and variance), to various popular wavelet based methods which do assume homoskedasticity. For illustration purposes, we also include the case where our method does assume homoskedasticity and takes an estimated $\s$ as input (this is also a feature of our method). Note that, for computational simplicity, we use a second order difference estimate of the variance as described by Hall et al. (1990) rather than the median absolute deviation (MAD) estimate that is commonly used in thresholding methods . The practical difference between these two estimators is small, unless the mean function is extremely irregular. Specifically, we include the following methods for this particular simulation study:

@@

\item TI thresholding using variance estimated by running MAD, Symmlet 8 basis (denoted by TI-thresh, RMAD, Symm8). See Gao (1997)
\item TI thresholding using variance estimated by SMASH, Symmlet 8 basis (denoted by TI-thresh, SMASH, Symm8)

@@

@@

\item Empirical Bayes shrinkage using MAD estimator, Symmlet 8 basis (denoted by PostMean, homo, Symm8). See Clyde \& George (1999,2000)

@@

\item TI thresholding using MAD estimator, Symmlet 8 basis (denoted by TI-thresh, homo, Symm8). See Coifman \& Donoho (1995)

@@

\item TI thresholding given true variance, Symmlet 8 basis (denoted by TI-thresh, truth, Symm8)

@@

Here compare our method mainly against TI thresholding, which often produced the smallest mean squared error (MSE) amongst all the methods discussed in the extensive simulation study conducted by Antoniadis et al. (2001). !!!!!!!!!!!!!!![describe these procedures earlier?]We also included three other adaptive methods, namely EbayesThresh by Johnstone \& Silverman (2005), the Empirical Bayes approach by Clyde \& George (1999,2000), as well as SureShrink, developed by Donoho \& Johnstone (1994). Note that methods (1)-(4) do not assume homoskedastic errors and perform their own variance estimation. In particular, we provide two ways to estimate the variance function in TI-thresholding: method (3) uses the running MAD approach as described in Gao (1997), and method (4) uses the variance estimate from SMASH. On the other hand, methods (5)-(9) all assume homoskedasticity and estimate a constant variance. Specifically, EbayesThresh places a Laplace prior on the wavelet coefficients, and we fix the scale parameter of the Laplace prior to be 0.5, as the marginal maximum likelihood implementation often fails to converge. The posterior mean is then taken to be the final estimate of the wavelet coefficients. Details for the Empirical Bayes approach by Clyde \& George (1999,2000), SureShrink, and homoskedastic TI-thresholding can be found in Antoniadis et al. (2001).  Further, we have ordered methods (5)-(9) in what we deem to be decreasing adaptivity. Finally, methods (10) and (11) are provided the true variance function and are included as benchmarks. Tables \ref{table:homo1} and \ref{table:homo3} displays the relative MSEs of various methods for the 7 test functions and 2 SNRs mentioned above, where the relative MSEs are the standard MSEs rescaled (for each test function and SNR) so that the baseline method has a MSE of 1. In our simulation study, the baseline method will be SMASH, using the Haar basis.
 %At the same time, we included SureShrink as it performs well in terms of mean square bias. We also compared our method against two other Bayesian approaches, of which the method described in Clyde \& George (1999,2000) was also included in Antoniadis et al. (2001) and performed well in terms of MSE. The other Bayesian approach, EbayesThresh, is more recent and and hence included as part of our study.
%Tables \ref{table:homo1} and \ref{table:homo3} displays the mean integrated squared error (MISE) of various methods for the 7 test functions and 2 SNRs mentioned above. Here MISE is defined as
%\begin{eqnarray}\label{eq:mise}
%MISE=\sum_{r=1}^R{\frac{10000*\sum_{i=1}^n(\hat{\mu}^{(r)}_i-\mu_i)^2}{\sum_{i=1}^n \mu_i^2}}
%\end{eqnarray}
%, which is simply the standard MSE rescaled in order to produce more comparable numbers. Here $R$ is the number of runs in each simulation (100 in our study) and $n$ is the sample size.

@@

SMASH, joint, Haar & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\
  SMASH, joint, Symm8 & 1.05 & 1.04 & 1.50 & 1.00 & 0.69 & 1.50 & 0.94 \\
  TI-thresh, RMAD, Symm8 & 2.03 & 2.38 & 3.34 & 1.63 & 1.17 & 2.34 & 1.28 \\
  TI-thresh, SMASH, Symm8 & 1.40 & 1.54 & 2.32 & 1.35 & 0.89 & 1.74 & 1.07 \\
  SMASH, homo, Symm8 & 1.05 & 1.05 & 1.53 & 1.00 & 0.71 & 1.51 & 0.94 \\
  Ebayes, homo, Symm8 & 1.30 & 1.01 & 1.49 & 1.16 & 0.77 & 1.66 & 1.09 \\
  PostMean, homo, Symm8 & 1.80 & 1.26 & 1.75 & 1.71 & 0.89 & 2.14 & 1.61 \\
  SURE, homo, Symm8 & 6.26 & 2.83 & 4.60 & 9.45 & 3.28 & 10.63 & 11.41 \\
  TI-thresh, homo, Symm8 & 1.47 & 1.64 & 2.39 & 1.37 & 0.90 & 1.74 & 1.08 \\
  SMASH, truth, Symm8 & 1.05 & 1.04 & 1.52 & 1.00 & 0.70 & 1.51 & 0.94 \\
  TI-thresh, truth, Symm8 & 1.45 & 1.59 & 2.35 & 1.36 & 0.90 & 1.72 & 1.07 \\

@@

\caption{Relative MSE of various methods for iid Gaussian errors, SNR=1}

@@

SMASH, joint, Haar & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\
  SMASH, joint, Symm8 & 0.82 & 1.41 & 3.20 & 0.77 & 0.54 & 1.72 & 0.69 \\
  TI-thresh, RMAD, Symm8 & 1.12 & 2.34 & 5.80 & 0.94 & 0.84 & 2.84 & 1.10 \\
  TI-thresh, SMASH, Symm8 & 0.88 & 1.39 & 4.03 & 0.85 & 0.60 & 1.85 & 0.83 \\
  SMASH, homo, Symm8 & 0.81 & 1.21 & 3.07 & 0.77 & 0.50 & 1.65 & 0.69 \\
  Ebayes, homo, Symm8 & 0.96 & 1.36 & 2.98 & 0.88 & 0.58 & 1.76 & 0.83 \\
  PostMean, homo, Symm8 & 1.28 & 1.69 & 3.63 & 1.18 & 0.70 & 2.54 & 1.13 \\
  SURE, homo, Symm8 & 3.38 & 3.45 & 7.39 & 5.05 & 2.11 & 10.14 & 6.34 \\
  TI-thresh, homo, Symm8 & 0.91 & 1.50 & 4.13 & 0.86 & 0.61 & 1.90 & 0.85 \\
  SMASH, truth, Symm8 & 0.81 & 1.15 & 2.86 & 0.77 & 0.50 & 1.63 & 0.69 \\
  TI-thresh, truth, Symm8 & 0.90 & 1.41 & 3.96 & 0.86 & 0.60 & 1.87 & 0.84 \\

@@

\caption{Relative MSE of various methods for iid Gaussian errors, SNR=3} 

@@

SMASH, joint, Haar & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\
  SMASH, joint, Symm8 & 1.02 & 0.91 & 1.23 & 1.38 & 0.71 & 1.27 & 0.90 \\
  TI-thresh, RMAD, Symm8 & 3.39 & 1.52 & 2.66 & 6.64 & 1.77 & 4.43 & 5.69 \\
  TI-thresh, SMASH, Symm8 & 1.83 & 1.46 & 1.97 & 1.84 & 0.93 & 1.56 & 1.03 \\
  SMASH, homo, Symm8 & 1.88 & 1.07 & 1.92 & 4.91 & 1.56 & 3.41 & 4.40 \\
  TI-thresh, homo, Symm8 & 8.66 & 2.79 & 6.73 & 29.84 & 7.15 & 19.45 & 29.05 \\
  SMASH, truth, Symm8 & 1.00 & 0.71 & 1.14 & 1.33 & 0.55 & 1.13 & 0.85 \\
  TI-thresh, truth, Symm8 & 1.88 & 1.22 & 1.81 & 1.83 & 0.78 & 1.42 & 1.04 \\

@@

\caption{Relative MSE of various methods for the Clipped Blocks variance function, SNR=1, Gaussian errors} 

@@

SMASH, joint, Haar & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\
  SMASH, joint, Symm8 & 0.83 & 1.26 & 2.34 & 1.11 & 0.45 & 1.90 & 0.72 \\
  TI-thresh, RMAD, Symm8 & 2.12 & 1.68 & 3.03 & 4.09 & 0.90 & 3.55 & 3.39 \\
  TI-thresh, SMASH, Symm8 & 0.98 & 1.48 & 3.17 & 1.32 & 0.50 & 2.17 & 0.84 \\
  SMASH, homo, Symm8 & 1.68 & 1.16 & 2.50 & 3.18 & 1.09 & 2.83 & 2.65 \\
  TI-thresh, homo, Symm8 & 6.72 & 2.34 & 5.18 & 17.54 & 3.61 & 13.22 & 16.13 \\
  SMASH, truth, Symm8 & 0.80 & 0.84 & 1.66 & 1.07 & 0.35 & 1.80 & 0.70 \\
  TI-thresh, truth, Symm8 & 0.99 & 1.15 & 2.34 & 1.29 & 0.38 & 2.11 & 0.83 \\

@@

\caption{Relative MSE of various methods for the Clipped Blocks variance function, SNR=3, Gaussian errors}

@@

SMASH, joint, Haar & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\
  SMASH, joint, Symm8 & 1.00 & 0.93 & 1.05 & 1.08 & 0.83 & 1.02 & 0.92 \\
  TI-thresh, RMAD, Symm8 & 5.52 & 2.00 & 3.71 & 7.88 & 4.08 & 6.70 & 7.72 \\
  TI-thresh, SMASH, Symm8 & 1.13 & 1.20 & 1.40 & 1.25 & 0.95 & 1.11 & 1.00 \\
  SMASH, homo, Symm8 & 5.11 & 1.85 & 3.35 & 7.07 & 3.81 & 6.07 & 6.90 \\
  TI-thresh, homo, Symm8 & 13.47 & 3.94 & 8.21 & 19.95 & 10.02 & 16.94 & 19.78 \\
  SMASH, truth, Symm8 & 0.45 & 0.93 & 0.72 & 0.41 & 0.39 & 0.47 & 0.28 \\
  TI-thresh, truth, Symm8 & 0.66 & 1.19 & 1.11 & 0.60 & 0.55 & 0.56 & 0.33 \\

@@

\caption{Relative MSE of various methods for the Bumps variance function, SNR=1, Gaussian errors}

@@

SMASH, joint, Haar & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\
  SMASH, joint, Symm8 & 0.83 & 0.87 & 1.23 & 0.98 & 0.66 & 1.33 & 0.86 \\
  TI-thresh, RMAD, Symm8 & 4.10 & 1.25 & 2.41 & 6.42 & 2.35 & 5.58 & 6.27 \\
  TI-thresh, SMASH, Symm8 & 0.88 & 1.14 & 1.60 & 1.12 & 0.67 & 1.60 & 0.95 \\
  SMASH, homo, Symm8 & 3.85 & 1.20 & 2.26 & 5.80 & 2.37 & 5.10 & 5.63 \\
  TI-thresh, homo, Symm8 & 9.95 & 2.06 & 4.60 & 16.02 & 5.52 & 13.50 & 15.85 \\
  SMASH, truth, Symm8 & 0.39 & 1.12 & 1.13 & 0.44 & 0.32 & 0.58 & 0.32 \\
  TI-thresh, truth, Symm8 & 0.45 & 1.65 & 1.39 & 0.60 & 0.41 & 0.72 & 0.37 \\

@@

\caption{Relative MSE of various methods for the Bumps variance function, SNR=3, Gaussian errors} 

@@

Summarizing the simulation studies conducted so far, we have demonstrated that our method does a reasonable job of mean and variance estimation for a variety of situations in the Gaussian case. As such, we now turn our attention to the Poisson case. For this simulation study, we considered different test functions and Poisson intensities for a given sample size of $n=1024$ as in Timmermann \& Nowak (1999) and Fryzlewicz \& Nason (2004), over 100 independent runs. Specifically, the ``Spikes'', ``Angles'', ``Bursts'',``Clipped Blocks'',``Bumps'' and ``Heavisine'' functions were chosen. The first 5 were part of a simulation study by Besbeas et al. (2004), and the ``Heavisine'' function was considered by Fryzlewicz \& Nason (2004). These test functions were then shifted and scaled to have (min,max) intensities of (0.01,3), (1/8,8) and (1/128,8), of which the latter two were the values used in Fryzlewicz \& Nason (2004). The low intensity scenario of (0.01,3) was chosen to reflect the small number of counts often present in certain types of high-throughput sequencing data, an application we will demonstrate in more detail later on. To assess the performance of our method, we used the same relative MSE as defined above for the Gaussian case, and considered the following methods in our simulation study:

@@

@@

The Haar-Fisz transform uses 50 external cyclespins as suggested by Fryzlewicz \& Nason (2004). The Anscombe transformations use the Symmlet 8 basis, while the Haar-Fisz transformation uses the Symmlet 10 basis, as recommended by the corresponding software. Out of the three Bayesian methods included in this simulation study, SMASH and BMSM both estimate the hyperparameters for their respective priors by maximum likelihood, while BMMIM uses fixed hyperparameters as recommended in Besbeas (2004). In addition, we also considered the conditional variance stabilization (CVS) approach described in Jansen (2006). However, we did not include the MSEs for CVS as we did not obtain sensible results, and are wary that we were misusing the software.  Except for BMSM and our method (which are entirely adaptive), we considered primary resolution levels of 4,5,6 and 7 for all other methods. We present the relative MSEs for test functions ``Angles'' and ``Bumps'' in Tables \ref{table:pois_angles} and \ref{table:pois_bumps} respectively; full simulation results can be found in Appendix \ref{}.\bigskip\\

@@

SMASH & 1.00 & 1.00 & 1.00 \\
  BMSM & 1.15 & 1.04 & 1.01 \\
  BMMIM & 1.53 & 1.49 & 21.99 \\
  Haar-Fisz & 2.05 & 2.47 & 4.36 \\
  Anscombe, universal & 2.61 & 2.80 & 4.24 \\
  Haar thresholds & 1.52 & 1.66 & 12.17 \\

@@

\caption{Relative MSE of various methods for the Clipped Blocks function for Poisson data} 
